MS_CNuptake.Rmd

### 2022-09-11 MS_CNuptake.Rmd
small update

@@

anpp_tnpp_dataset_grass <- na.omit(grassland_sitemean[,c("anpp_tnpp_a","Tg_a","PPFD_a","vpd_a","CNrt_a","fAPAR_a")])
model_g2 <- stepwise_lm(anpp_tnpp_dataset_grass,"anpp_tnpp_a")
model_g2[[1]]
summary(lm(anpp_tnpp_a~Tg_a,data=anpp_tnpp_dataset_grass))
#non-significant! so alternatively using constant ratio
summary((lm(anpp_a~-1+tnpp_a,data=grassland_sitemean))) # 0.49 for anpp, so 0.51 for bnpp

>>>>

#check some percentage
dim(subset(NPP_all, is.na(Nmin)==T & pft =="Forest"))
dim(subset(NPP_all, is.na(Nmin)==T & pft =="Grassland"))

dim(subset(NPP_all, is.na(Nmin)==T & lat<=23.5 & lat>=-23.5)) 
dim(subset(NPP_all, is.na(Nmin)==T & lat<=50 & lat>23.5))
dim(subset(NPP_all, is.na(Nmin)==T & lat>= -50 & lat< -23.5))
dim(subset(NPP_all, is.na(Nmin)==T ))

@@

anpp_tnpp_dataset_grass <- na.omit(grassland_sitemean[,c("anpp_tnpp_a","Tg_a","PPFD_a","vpd_a","CNrt_a","fAPAR_a")])
model_g2 <- stepwise_lm(anpp_tnpp_dataset_grass,"anpp_tnpp_a")
model_g2[[1]]
summary(lm(anpp_tnpp_a~Tg_a,data=anpp_tnpp_dataset_grass))
#non-significant! so alternatively using constant ratio
summary((lm(anpp_a~-1+tnpp_a,data=grassland_sitemean))) # 0.50
